Model Checking

### 2023-05-26 owen/Write Ups/03_existing_models.qmd
identifying potential problems with the model

@@

chessdotcom_hikaru_recent <- get_raw_chessdotcom(usernames = "Hikaru",
                                                 year_month = c(202201:202205))

jan_games <- top_bullet$username %>% 
  map_dfr(~get_raw_chessdotcom(.x, year_month = 202201))

top_games <- jan_games %>% 
  filter(White %in% top_bullet$username) %>% 
  filter(Black %in% top_bullet$username)

@@

top_games %>% 
  filter(TimeClass == "blitz")

>>>>

```{r}
stan_fit <- readRDS("../cluster_scripts/Cluster_stan.RDS")

mcmc_hist(stan_fit$draws(c("alpha[1]", "alpha[2]")))

r_hat <- rhat(stan_fit)

summary(r_hat)

which(r_hat > 1.15)
## just problems with mu and tau for convergence here, otherwise good?

@@

# chessdotcom_hikaru_recent <- get_raw_chessdotcom(usernames = "Hikaru",
#                                                  year_month = c(202201:202205))

games_22 <- top_bullet$username %>% 
  map_dfr(~get_raw_chessdotcom(.x, year_month = c(202201:202203)))

top_games <- games_22 %>% 
  filter(White %in% top_bullet$username) %>% 
  filter(Black %in% top_bullet$username)

@@

bullet_games <- top_games %>% 
  filter(TimeClass == "bullet")

bullet_top10 <- saveRDS(bullet_games, file = "chess_com_bullet_10.RDS")
